### 2021-11-17 paper/output/document/paper33.tex
what am i doing

The results presented below are summarized in Figure \ref{fig:goalstable}. For each goal, I indicate which 
interpretations successfully meet that goal. The fact that my custom formalization meets all the goals
indicates that it improves on prior formalization attempts. Below I will explain and justify
the goals.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{figure}
\centering
\includegraphics[scale=0.4]{goalstable.png}
\caption{Table indicating which goals are met by the naive formalization, Kroy's formalization, and 
the custom formalization respectively..} \label{fig:goalstable}
\end{figure}
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Goals From Prior Attempts \label{sec:priorgoals}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
\textbf{FUL Stronger than DDL} One simple objective that the naive formalization failed to meet is the fact that the FUL should
not hold in the base logic (DDL). Recall that the naive formalization of the FUL\footnote{
This formalization reads $\vDash ((\neg (\square P \{A\})) \longrightarrow O \{\neg A\})$.} held in the 
base logic, so adding it as an axiom didn't make the logic any stronger. This is troubling 
because the base logic does not come equipped with the categorical imperative built-in. It 
defines basic properties of obligation, such as ought implies can, but contains no axioms that represent
the formula of universal law. Therefore, if a formalization of the FUL holds in the 
base logic, then it is too weak to actually represent the FUL. The naive interpretation holds in DDL but Kroy's formalization
does not. Because the naive interpretation is no stronger than DDL, it is acts a control group equivalent
to DDL itself.

>>>>

The results presented below are summarized in Figure \ref{fig:goalstable}. For each goal, I indicate which 
interpretations successfully meet that goal. The fact that my custom formalization meets all the goals
indicates that it improves on prior formalization attempts. Below I will explain and justify
the goals.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{figure}
\centering
\includegraphics[scale=0.4]{goalstable.png}
\caption{Table indicating which goals are met by the naive formalization, Kroy's formalization, and 
the custom formalization respectively.} \label{fig:goalstable}
\end{figure}
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Goals From Prior Attempts \label{sec:priorgoals}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
\textbf{FUL Stronger than DDL} One simple objective that the naive formalization failed to meet is the fact that the FUL should
not hold in the base logic (DDL). Recall that the naive formalization of the FUL\footnote{
This formalization reads $\vDash ((\neg (\square P \{A\})) \longrightarrow O \{\neg A\})$.} held in the 
base logic, so adding it as an axiom didn't make the logic any stronger. This is troubling 
because the base logic does not come equipped with the categorical imperative built-in. It 
defines basic properties of obligation, such as ought implies can, but contains no axioms that represent
the formula of universal law. Therefore, if a formalization of the FUL holds in the 
base logic, then it is too weak to actually represent the FUL. The naive interpretation holds in DDL but Kroy's formalization
does not. Because the naive interpretation is no stronger than DDL, it is acts a control group equivalent
to DDL itself.
